Risk Perceptions for Wearable Devices

### 2015-03-05 tex-inputs/conclusion.tex
fixed little compiling bugs
rough draft done

We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices. We examine how upset participants would in  304 scenarios, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns. We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model. An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology. We also state what users perceived as the most significant concerns with respect to wearable devices. We conclude by discussing future research directions in the wearables and user study space.

>>>>

Our 1,784 Internet users for their perceptions of wearable devices was the first large-scale study to investigate user security and privacy concerns for wearable devices. We identify that participants are most concerned about protecting their financial information, photos, and videos and least concerned about demographic or biometric data. We find that participants have a significant difference in perception of risk when data is being shared with an application's server versus other human recipients, and also that certain data is more comfortably shared with certain recipients. Participants' self-reported concerns of categories and perceptions of new wearable device capabilities are also presented to give a sense of the relevant user concerns, which can be used to guide future research in privacy with respect to wearable devices, especially warnings, notifications, and permissions. We perform two regression model analyses with respect to the type of data and the associated risks.
